---
title: 'MSCS 264: Homework #13'
subtitle: 'Due Tues Nov 20 at 11:59 PM'
output:
  pdf_document:
    fig_height: 4
    fig_width: 5
  html_document: default
  word_document: default
editor_options: 
  chunk_output_type: console
---

You should submit a knitted pdf file on Moodle, but be sure to show all of your R code, in addition to your output, plots, and written responses.

```{r, setup, include=FALSE}
library(tidyverse)
library(stringr)
library(rvest)
library(httr)
```

##Web scraping

1. Read in the table of data found at https://en.wikipedia.org/wiki/List_of_United_States_cities_by_crime_rate and create a plot showing violent crime rate (total violent crime) vs. property crime rate (total property crime).  Identify outlier cities (those with "extreme" values for `VCrate` and/or `PCrate`) by feeding a data set of outliers into `geom_label_repel()`.

Hints:

- after reading in the table using `html_table()`, create a data frame with just the columns you want, using a command such as: `crimes3 <- as.data.frame(crimes2)[,c(LIST OF COLUMN NUMBERS)]`.  Otherwise, R gets confused since it appears as if several columns all have the same column name.
- then, turn `crimes3` into a tibble with `as.tibble(crimes3)` and do necessary tidying: get rid of unneeded rows, parse columns into proper format, etc.

```{r}

crime <- read_html("https://en.wikipedia.org/wiki/List_of_United_States_cities_by_crime_rate")
crimetable <- html_nodes(crime, css = "table") 
crimedata <- html_table(crimetable, header = TRUE, fill = TRUE)[[2]]
crimedata1 <- as.data.frame(crimedata)[,c(1,2,4,10)]
crimedata2 <- as.tibble(crimedata1)

crimedatatidy <- crimedata2 %>%
  rename(`Violent_Crime` = "Violent Crime",
         `Property_Crime` = "Property Crime") %>%
  mutate(Violent_Crime_Rate = parse_double(Violent_Crime),
         Property_Crime_Rate = parse_double(Property_Crime)) %>%
  select(State, City, Violent_Crime_Rate, Property_Crime_Rate)
  
crimedatatidy1 <- crimedatatidy[-c(1), ] %>%
  arrange(State)

crimedatatidy1

outliercrime <- crimedatatidy1 %>%
  filter(Violent_Crime_Rate >= 1000, Property_Crime_Rate >= 1240)

ggplot(data = crimedatatidy1,aes(x = Violent_Crime_Rate, y = Property_Crime_Rate)) +
  geom_point() +
  ggrepel::geom_label_repel(aes(label = City, colour = City), data = outliercrime, show.legend = FALSE)
  
```

2. As we did in class, use the `rvest` package to pull off data from imdb's top grossing films released in 2017 at https://www.imdb.com/search/title?year=2017&title_type=feature&sort=boxoffice_gross_us,desc.  Create a tibble that contains the title, gross, imdbscore, and metascore for the top 50 films.  Then generate a scatterplot of one of the ratings vs. gross, labelling outliers as in Question 1 with the title of the movie.

```{r}

top50 <- read_html("https://www.imdb.com/search/title?title_type=feature&year=2017-01-01,2017-12-31&sort=boxoffice_gross_us,desc")
top50
title <- html_nodes(top50, ".lister-item-header a")
title1 <- html_text(title)
title1
gross <- html_nodes(top50, ".ghost~ .text-muted+ span")
gross1 <- html_text(gross)
gross2 <- parse_number(gross1)
gross2
metascore <-  html_nodes(top50, ".ratings-metascore")
metascore1 <- html_text(metascore)
metascore2 <- parse_number(metascore1)
metascore2
imdbscore <- html_nodes(top50, ".ratings-imdb-rating strong")  
imdbscore1 <- parse_number(html_text(imdbscore))
imdbscore1


top50table <- tibble(title1, gross2, metascore2, imdbscore1)
top50table %>%
  rename("Title" = title1, "Gross" = gross2, "Metascore" = metascore2, "Imdb Score" = imdbscore1)

outliermovie <- top50table %>%
  filter(gross2 >= 350)

ggplot(data = top50table, aes(x = metascore2, y = gross2)) +
  geom_point() +
  geom_smooth() +
  ggrepel::geom_label_repel(aes(label = title1, colour = title1), data = outliermovie, show.legend = FALSE) +
  labs(x = "Metascore", y = "Gross (in millions)")
  
```

3. 5 points if you push your Rmd file with HW13 solutions along with the knitted pdf file to your MSCS264-HW13 repository in your GitHub account.  So that I can check, make your repository private (good practice when doing HW), but add me (username = proback) as a collaborator under Settings > Collaborators.

Done.

##Factors

Read Chapter 15 on factors and attempt the following problems:

4. In the `nycflights13` data, just consider flights to O'Hare (dest=="ORD"), and summarize the mean arrival delay by carrier (actually use the entire name of the carrier after merging carrier names into `flights`).  Then use `geom_point` to plot mean arrival delay vs. carrier - first without reordering carrier names, and second after reordering carrier names by mean arrival delay.

```{r}
library(nycflights13)

oharedelay <- flights %>%
  filter(dest == "ORD") %>%
  left_join(airlines, by = "carrier") %>%
  group_by(name) %>%
  summarise(av_arr_delay = mean(arr_delay, na.rm = TRUE))

oharedelay

ggplot(data = oharedelay, aes(x = av_arr_delay, y = name)) +
  geom_point()

oharedelay %>%
  mutate(name1 = fct_reorder(name, av_arr_delay)) %>%
  ggplot(aes(x = av_arr_delay, y = name1)) +
  geom_point()

```

5. Again considering only flights to O'Hare, create a new factor variable which differentiates national carriers (American and United) from regional carriers (all others which fly to O'Hare).  Then create a violin plot comparing arrival delays for all flights to O'Hare from those two groups (you might want to exclude arrival delays over a certain level).

```{r}

flights %>%
   filter(dest == "ORD") %>%
  left_join(airlines, by = "carrier") %>%
  count(name)
  

oharedelay1 <- flights %>%
  filter(dest == "ORD") %>%
  left_join(airlines, by = "carrier") %>%
  mutate(name = fct_collapse(name,
                             nationalcarriers = c("American Airlines Inc.", "United Air Lines Inc."),
                             regionalcarriers = c("Endeavor Air Inc.", "Envoy Air", "ExpressJet Airlines Inc.",
                                                  "JetBlue Airways", "SkyWest Airlines Inc."))) %>%
  select(name, arr_delay)

oharedelay2 <- oharedelay1 %>%
  filter(arr_delay <= 300) 

ggplot(data = oharedelay2, aes(x = name, y = arr_delay)) +
  geom_violin()

```

